Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-22 paper-2023-acsos-pulverization.tex
Increase char spacing in sources + readjust a bit

\lstdefinelanguage{pulv}[]{Kotlin}{
 basicstyle=\small\ttfamily\lst@ifdisplaystyle\footnotesize\fi,
%	frame=single,
%	escapechar=\%,
%  keywordstyle=\color{blue},
  keywordstyle=[3]\bfseries{},
  keywords=[3]{pulverizedSystem,device,and,deployableOn,pulverizationRuntime,startsOn,onDevice,reconfigurationRules,reconfigures,movesTo},
%  emph={DeviceBehaviour,DeviceCommunication,DeviceSensors,DeviceActuators,HighLoad,LowBattery},
%  sensitive=true,
%  morecomment=[l]{//},
%  morecomment=[n]{/*}{*/},
%  commentstyle=\color{green!40!black},
%  morestring=[b]",
%  morestring=[b]',
%  morestring=[b]""",
%  stringstyle=\ttfamily\color{orange},
}
\lstset{language=pulv,
basewidth=0.52em % decreases spacing between chars
}

@@

\begin{lstlisting}[
    float=ht,
    numbers=left,
    language=pulv,
    caption={
        Example of the usage of the domain-specific language for the runtime configuration.
        The example defines the runtime configuration of the system, specifying the initial deployment and the reconfiguration rules.
    },
    label=lst:runtime-configuration,
    numbers=left,
    escapechar=\%
]
// Reconfiguration events %\label{code:reconfigev:start}%
expect fun cpuLoad(): Flow<Double>
expect fun batteryLevel(): Flow<Double>
object HighLoad : ReconfigurationEvent<Double>() {
  override val predicate = { it > 0.90 }
  override val events = cpuLoad()
}
object LowBattery : ReconfigurationEvent<Double>() {
  override val predicate = { it < 0.20 }
  override val events = batteryLevel()
}%\label{code:reconfigev:end}%
// Available hosts %\label{code:hosts:start}%
object Smartphone : Host {
  override val hostname = "smartphone"
  override val capabilities = setOf(EmbeddedDevice)
}
object Server : Host {
  override val hostname = "amazon-aws"
  override val capabilities=setOf(HighCPU,LowLatencyComm)
}%\label{code:hosts:end}%
// Runtime initial setup and runtime reconfiguration rules %\label{code:infra:start}%
val infrastructure = setOf(Smartphone, Server)
val conf = ... // see %\crefe{lst:system-configuration}%
pulverizationRuntime(conf, "iot-sensor", infrastructure) {
  DeviceBehaviour() startsOn Server%\label{code:mapping:start}%
  DeviceCommunication() startsOn Server
  DeviceSensors() startsOn Smartphone
  DeviceActuators() startsOn Smartphone%\label{code:mapping:end}%
  reconfigurationRules {%\label{code:reconfig:start}%
    onDevice {
      HighLoad reconfigures {Behaviour movesTo Smartphone}
      LowBattery reconfigures {Behaviour movesTo Server}
    }
  }%\label{code:reconfig:end}%
}%\label{code:infra:end}%
pulverizationRuntime(conf, "control-center", infrastructure) {
  /* ... */
}
\end{lstlisting}

>>>>

\lstdefinelanguage{pulv}[]{Kotlin}{
 basicstyle=\small\ttfamily\lst@ifdisplaystyle\footnotesize\fi,
%	frame=single,
%	escapechar=\%,
%  keywordstyle=\color{blue},
  keywordstyle=[3]\bfseries{},
  keywords=[3]{pulverizedSystem,device,and,deployableOn,pulverizationRuntime,startsOn,onDevice,reconfigurationRules,reconfigures,movesTo},
%  emph={DeviceBehaviour,DeviceCommunication,DeviceSensors,DeviceActuators,HighLoad,LowBattery},
%  sensitive=true,
%  morecomment=[l]{//},
%  morecomment=[n]{/*}{*/},
%  commentstyle=\color{green!40!black},
%  morestring=[b]",
%  morestring=[b]',
%  morestring=[b]""",
%  stringstyle=\ttfamily\color{orange},
}
\lstset{language=pulv,
basewidth=0.55em % decreases spacing between chars
}

@@

\begin{lstlisting}[
    float=ht,
    numbers=left,
    language=pulv,
    caption={
        Example of the usage of the domain-specific language for the runtime configuration.
        The example defines the runtime configuration of the system, specifying the initial deployment and the reconfiguration rules.
    },
    label=lst:runtime-configuration,
    numbers=left,
    escapechar=\%
]
// Reconfiguration events %\label{code:reconfigev:start}%
expect fun cpuLoad(): Flow<Double>
expect fun batteryLevel(): Flow<Double>
object HighLoad : ReconfigurationEvent<Double>() {
  override val predicate = { it > 0.90 }
  override val events = cpuLoad()
}
object LowBattery : ReconfigurationEvent<Double>() {
  override val predicate = { it < 0.20 }
  override val events = batteryLevel()
}%\label{code:reconfigev:end}%
// Available hosts %\label{code:hosts:start}%
object Smartphone : Host {
  override val hostname = "smartphone"
  override val capabilities = setOf(EmbeddedDevice)
}
object Server : Host {
  override val hostname = "amazon-aws"
  override val capabilities = 
    setOf(HighCPU,LowLatencyComm)
}%\label{code:hosts:end}%
// Runtime initial setup and runtime reconfig. rules %\label{code:infra:start}%
val infrastructure = setOf(Smartphone, Server)
val conf = ... // see %\crefe{lst:system-configuration}%
pulverizationRuntime(conf,"iot-sensor",infrastructure){
  DeviceBehaviour() startsOn Server%\label{code:mapping:start}%
  DeviceCommunication() startsOn Server
  DeviceSensors() startsOn Smartphone
  DeviceActuators() startsOn Smartphone%\label{code:mapping:end}%
  reconfigurationRules {%\label{code:reconfig:start}%
    onDevice {
      HighLoad reconfigures 
        { Behaviour movesTo Smartphone }
      LowBattery reconfigures 
        { Behaviour movesTo Server }
    }
  }%\label{code:reconfig:end}%
}%\label{code:infra:end}%
pulverizationRuntime(conf, "control-center", infrastructure) {
  /* ... */
}
\end{lstlisting}
